\bf\mftitle

### 2011-02-27 doc/jInfer/projecttype/projecttype.tex
#3187361 projecttype doc

First of the two actions, after it was invoked, open file choose dialog which has set file filter according to available classes that implement \code{Processor} interface registered in jInfer with \code{ServiceProvider}. After selecting files in dialog, these files are inserted into particular \emph{input file} node according to mapping of file extension to folder type gained from \code{Processor} classes.\\

@@

@@

@@

\subsection{Preferences}

>>>>

First of the two actions, after it was invoked, file choose dialog is opened which has set file filter according to available classes that implement \code{Processor} interface registered in jInfer with \code{ServiceProvider}. After selecting files in dialog, these files are inserted into particular \emph{input file} node according to mapping of file extension to folder type gained from \code{Processor} classes. If no mapping for some extension exists, this file is inserted into folder which is defined in \emph{Miscellaneous} properties category (section \ref{pref}).\\

@@

\noindent Example of the implemented \code{PropertiesPanelProvider}.

\begin{verbatim}
@ServiceProvider(service = PropertiesPanelProvider.class)
public class PropertiesPanelProviderImpl implements PropertiesPanelProvider{

  @Override
  public AbstractPropertiesPanel getPanel(final Properties properties) {
    return new ExamplePropertiesPanel(properties);
  }

  @Override
  public String getName() {
    return "exampleCategoryID";
  }

  @Override
  public String getDisplayName() {
    return "Example category";
  }

  @Override
  public int getPriority() {
    return 1000;
  }

  @Override
  public String getParent() {
    return null;
  }

  @Override
  public List<VirtualCategoryPanel> getSubCategories() {
    final List<VirtualCategoryPanel> result = new ArrayList<VirtualCategoryPanel>();
    result.add(new VirtualCategoryPanel("virtual_categoryID", "example virtual category",
            ModuleSelectionHelper.lookupImpls(IGGenerator.class)));

    return result;
  }
\end{verbatim}

@@

\noindent Example of the implemented \code{AbstractPropertiesPanel}.

\begin{verbatim}
public class ProjectPropertiesPanel extends AbstractPropertiesPanel {

  private javax.swing.JCheckBox checkBox;

  public ProjectPropertiesPanel(final Properties properties) {
    super(properties);
    init();
  }

  public void init() {
    ...
    initialize checkBox
    ...
  }

  @Override
  public void store() {
    properties.setProperty("some_property", Boolean.toString(checkBox.isSelected()));
  }

  @Override
  public void load() {
    checkBox.setSelected(Boolean.parseBoolean(properties.getProperty("some_property", "true")));
  }
}
\end{verbatim}

@@

This section describes ability of jInfer to create new jInfer project through \emph{new project} wizard. This wizard contains two steps, where first is standard one with project name and location selection, and the second is the selection of Initial grammar module, Simplifier and Schema generator module which will be used in inference for newly created module. In the new project creation process can be already finished in a first step, in that case, default modules will be used for inference. After finishing of the wizard, new jInfer project type is created with typed name in selected location. It is important to notice that package \code{cz.cuni.mff.ksi.jinfer.projecttype} contains \code{JInferTemplateProject.zip} file, in which is default folder structure of the jInfer project type, and the content of a zip is copied into location defined in the wizard. For more information, how to create new project wizard,  please look at \cite{project_sample}.\\

All classes responsible for creation of this wizard are in package \code{cz.cuni.mff.ksi.jinfer.projecttype.sample}. It contains \code{JinferTemplateWizardIterator} class which defines number of steps in the wizard and creates panel for each step. Each step is  represented by a class implementing \code{WizardDescriptor.Panel} interface, which creates steps panel and validate its data inserted by a user. Finally there is class extending \code{JPanel} in which are components of the first step.

\subsection{Preferences}\label{pref}

Also jInfer project type has its own properties category in a project properties window and is called \emph{Miscellaneous}. In this category,
two properties can be set. First property is default \emph{input file} folder to which is inserted input file selected from \emph{FilesAddAction}, that has extension, which is not defined by any \code{Processor} registered in jInfer. Second property is global \emph{LOG} level, which defines the minimum level of messages that will be displayed in jInfer output window. If some module has its own \emph{LOG} level setting, global settings are overridden by these.
